Hydra battles in Coq

### 2020-10-26 doc/hydras.tex
typos in the index

\label{types:T1}
\index{Constants!zero:T1}

@@

\label{types:T2}
\emph{Please look also at the library
\href{../src/html/hydras.Gamma0.T2.html}{Gamma0.T2.html}}.

@@

\label{sect:omega-T1}
\index{Constants!zero:T1}

@@

Like in Chapter~\ref{chap:T1}, we define an inductive type with two constructors, one for $0$, the other for the construction $\psi(\alpha,\beta)\times(n+1)+\gamma$, adapting a Manolios-Vroon-like notation~\cite{Manolios2005} to
\emph{Veblen normal forms}.

@@

The enumeration function of critical ordinals, presented in Sect.\~vref{sect:phi-schutte}, is recursively defined in type \texttt{T2}.

@@

\begin{Coqsrc}
Class G0 := mkg0 {vnf : T2; vnf_ok : nfb vnf}.

>>>>

\label{types:T1}
%\index{Constants!zero:T1}

@@

\emph{Please look also at the library
\href{../src/html/hydras.Gamma0.T2.html}{Gamma0.T2.html}}.

@@

\label{sect:omega-T1}
%\index{Constants!zero:T1}

@@

Like in Chapter~\ref{chap:T1}, we define an inductive type with two constructors, one for $0$, the other for the construction $\psi(\alpha,\beta)\times(n+1)+\gamma$, adapting a Manolios-Vroon-like notation~\cite{Manolios2005} to
\emph{Veblen normal forms}.
\label{types:T2}

@@

The enumeration function of critical ordinals, presented in Sect.~\vref{sect:phi-schutte}, is recursively defined in type \texttt{T2}.

@@

\begin{Coqsrc}
Module G0.

Class G0 := mkg0 {vnf : T2; vnf_ok : nfb vnf}.
